Empirical Evaluation of eval in R

### 2020-08-22 inst/analysis/analysis_stable.Rmd
Degree of polymorphism

---
title: "Empirical Evaluation of eval in R"
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
    data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.5/deduplicated_more_calls.fst"
    #data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-all.1/calls.fst"
    # The trace data on all CRAN does not have all the columns of the smaller corpus. The analysis will fail for the big corpus.

@@

>>>>

---
title: "Empirical Evaluation of eval in R"
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
    data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.5/summarized-packages.fst"
    #data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-all.1/calls.fst"
    # The trace data on all CRAN does not have all the columns of the smaller corpus. The analysis will fail for the big corpus.

@@

Another interesting figure is the degreee of polymorphism of the `expr` argument: how many different types (for `expr_resolved`) are there for one call sites?

```{r polymorphism_callsite}
expr_resolved_polymorphism <- eval_calls %>% group_by(eval_call_srcref) %>%
        summarise(polym_degree = vec_unique_count(expr_resolved_type))
```

```{r}
expr_resolved_polymorphism %>% ggplot() +
  geom_bar(aes(x = polym_degree)) +
  scale_x_continuous(breaks=c(0, 1, 5, 10)) +
  labs(title = "Degree of polymorphism", x = "degree", y = "n") 
```
